Deep Learning Project

### 2024-10-10 project/paper.tex
Changed red text to black.

\textcolor{red}{
\section {Motivation}
Attempting to reproduce the experiment from the Szegedy paper is primarily motivated by the desire to apply TensorFlow to a practical problem, such as image classification, using a realistic dataset. Recognizing that the operational environment would be constrained (i.e., running the reproduction on a desktop PC), we also saw this as an opportunity to evaluate the network's performance on a smaller version of the ImageNet dataset. This project allowed us to directly experience the challenges of training a neural network. Additionally, it provided valuable experience in writing TensorFlow code for a complex neural network with branching and joining structures, whereas our prior work has been limited to simpler, sequential networks.}

\textcolor{red}{
\section{Inspiration}
Two code bases served as the inspiration for our Tensorflow implementation of Inception. The image pre-processing, particularly regularization techniques were guided by \cite{dishasai_multiclass_classification}. The Inception layer implementation was inspired by \cite{googlenet_inception_module}. Lastly, the graphs in Figures \ref{fig:googlenet-simple-accuracy} and \ref{fig:googlenet-complex-accuracy} were inspired by \cite{datacamp_cnn_tensorflow}.}

>>>>

\section {Motivation}
Attempting to reproduce the experiment from the Szegedy paper is primarily motivated by the desire to apply TensorFlow to a practical problem, such as image classification, using a realistic dataset. Recognizing that the operational environment would be constrained (i.e., running the reproduction on a desktop PC), we also saw this as an opportunity to evaluate the network's performance on a smaller version of the ImageNet dataset. This project allowed us to directly experience the challenges of training a neural network. Additionally, it provided valuable experience in writing TensorFlow code for a complex neural network with branching and joining structures, whereas our prior work has been limited to simpler, sequential networks.

\section{Inspiration}
Two code bases served as the inspiration for our Tensorflow implementation of Inception. The image pre-processing, particularly regularization techniques were guided by \cite{dishasai_multiclass_classification}. The Inception layer implementation was inspired by \cite{googlenet_inception_module}. Lastly, the graphs in Figures \ref{fig:googlenet-simple-accuracy} and \ref{fig:googlenet-complex-accuracy} were inspired by \cite{datacamp_cnn_tensorflow}.
